\begin{thebibliography}{10}

\bibitem{sumo2011}
Behrisch, M., Bieker, L., Erdmann, J., Krajzewicz, D.:
SUMO---Simulation of Urban MObility: An Overview.
In: Proceedings of SIMUL (2011)

\bibitem{traci2018}
L{\'o}pez, P.A., et al.:
Microscopic Traffic Simulation using SUMO.
In: The SUMO traffic simulation in 21 days (2018)

\bibitem{osm}
OpenStreetMap contributors: \url{https://www.openstreetmap.org}.
Accessed 2026

\bibitem{modica2024eta}
Modica, T., Tappia, E., Colicchia, C., Melacini, M.:
Integrating arrival time estimation in truck scheduling: an explorative study in grocery retailing.
Production \& Manufacturing Research 12(1), Article 2425678 (2024).
\url{https://doi.org/10.1080/21693277.2024.2425678}

\bibitem{yu2017trafficpred}
Yu, J.J.Q., Gu, Y., Li, H., Li, S.:
A survey on traffic prediction using big data.
IEEE Transactions on Intelligent Transportation Systems 18(10), 2570--2586 (2017)

\bibitem{stgcn2018}
Yu, B., Yin, H., Zhu, Z.:
Spatio-Temporal Graph Convolutional Networks: A Deep Learning Framework for Traffic Forecasting.
In: Proceedings of IJCAI (2018)

\bibitem{dcrnn2018}
Li, Y., Yu, R., Shahabi, C., Liu, Y.:
Diffusion Convolutional Recurrent Neural Network: Data-Driven Traffic Forecasting.
In: Proceedings of ICLR (2018)

\bibitem{googlemapseta2021}
Derrow-Pinion, A., She, J., Wong, D., Lange, O., Hester, T., Perez, L., Nunkesser, M., Lee, S., Guo, X., Wiltshire, B., Battaglia, P.W., Gupta, V., Li, A., Xu, Z., Sanchez-Gonzalez, A., Li, Y., Veli\v{c}kovi\'c, P.:
ETA prediction with graph neural networks in Google Maps.
In: Proceedings of the 30th ACM International Conference on Information and Knowledge Management, pp.\ 3767--3776 (2021)

\bibitem{libcity2021}
Wang, J., Jiang, J., Jiang, W., Li, C., Zhao, W.X.:
LibCity: An open library for traffic prediction.
In: Proceedings of the 29th International Conference on Advances in Geographic Information Systems, pp.\ 145--148 (2021)

\bibitem{voloch2021}
Voloch, N., Voloch-Bloch, N.:
Finding the fastest navigation route by real-time future traffic estimations.
In: Proceedings of the IEEE International Conference on Microwaves, Communications, Antennas and Electronic Systems (COMCAS) (2021)

\bibitem{voloch2025}
Voloch, N., Penkar, N., Tordjman, G.:
Estimating accurate traffic time by smart simulative route predictions.
In: Proceedings of the 24th IFIP Conference on e-Business, e-Services and e-Society (I3E), Limassol, Cyprus (2025)

\bibitem{nids2026}
NiDS 2026 --- 6th International Conference on Novel and Intelligent Digital Systems.
University of West Attica, Athens, Greece, 23--25 September 2026.
\url{https://nids2026.uniwa.gr/}

\end{thebibliography}
