\begin{center}
{\large\bfseries Abstract}
\end{center}

\vspace{1em}

This project successfully developed a comprehensive real-time browser-based testing system for actual time of arrival prediction using Graph Neural Networks. The system is comprised of two main components: (1) a dataset generator and EDA analyzer for creating and analyzing traffic simulation datasets, and (2) a browser-based simulation player with model inference testing and statistical analysis capabilities.

The system allows any user to configure traffic simulations according to their specific needs, analyze the simulation data through comprehensive exploratory data analysis, create training datasets, train custom models using these datasets, and seamlessly plug in the dataset and trained model into the browser-based application for demonstrations and real-time testing. The dataset generator integrates SUMO traffic simulation to extract dynamic spatio-temporal graphs, providing flexible and comprehensive datasets for training and evaluation. The EDA analyzer performs exploratory data analysis on the generated datasets to understand feature distributions and patterns.

The browser-based simulation player enables real-time evaluation of predictions through an intuitive interface integrated with SUMO traffic simulation, allowing users to test model inference on live traffic scenarios and analyze results through statistical analysis dashboards. Key achievements include successful deployment of the model inference system with sub-100ms latency, implementation of real-time traffic simulation integration, and development of an accessible browser-based interface for interactive route selection, visualization, and performance analysis. The system serves as a valuable tool for researchers and practitioners in intelligent transportation systems, bridging the gap between theoretical research and practical application.

\vspace{1em}

\noindent\textbf{Keywords:} Graph Neural Networks, Time of Arrival Prediction, Traffic Simulation, SUMO, Real-Time Systems, Browser-Based Testing, Dataset Generation, Statistical Analysis

