\section{Introduction}

\subsection{Project Background}

Accurate Estimated Time of Arrival (ETA) prediction is fundamental to modern navigation systems and intelligent transportation applications. The DSTRA-GNN model, developed in previous research, represents a significant advancement in this field by integrating vehicle-level dynamics, junction states, and explicit route intent within a unified Mixture-of-Experts framework.

The model achieved remarkable performance improvements, reducing Mean Absolute Error (MAE) from 260 seconds to 46 seconds (82\% improvement) on large-scale simulated traffic datasets. However, while the model demonstrated excellent performance in offline evaluation scenarios, there was a critical need for real-time testing capabilities that allow users to interact with the model and evaluate its performance in realistic traffic conditions.

This project addresses this need by creating a comprehensive web-based platform that enables real-time testing and evaluation of ETA prediction models in realistic traffic simulations.

\subsection{Project Objectives}

The project aimed to achieve the following objectives:

\subsubsection{Primary Objectives}
\begin{enumerate}
    \item Develop a real-time web-based testing system for DSTRA-GNN models
    \item Integrate SUMO traffic simulation with the DSTRA-GNN model
    \item Create an interactive web interface for user route planning and ETA prediction
    \item Implement real-time data collection and statistical analysis capabilities
    \item Build a comprehensive database system for storing and analyzing prediction results
\end{enumerate}

\subsubsection{Secondary Objectives}
\begin{enumerate}
    \item Develop visualization tools for real-time traffic monitoring
    \item Create automated reporting systems for model performance evaluation
    \item Implement user authentication and session management
    \item Design responsive web interface for multiple device compatibility
    \item Establish API endpoints for potential integration with external systems
\end{enumerate}

\subsection{Project Scope}

The project scope encompasses:
\begin{itemize}
    \item Full-stack web application development
    \item Integration with SUMO traffic simulation engine
    \item Deployment of DSTRA-GNN model inference service
    \item Real-time data streaming and visualization
    \item Comprehensive testing and documentation
    \item Performance optimization and scalability considerations
\end{itemize}

\subsection{Document Structure}

This report is organized as follows: Chapter 2 reviews relevant literature in graph neural networks, traffic simulation, and web-based traffic systems. Chapter 3 describes the system architecture and design decisions. Chapter 4 details the implementation of each component. Chapter 5 presents testing methodologies and validation results. Chapter 6 discusses the results and achievements. Finally, Chapter 7 provides conclusions and future work directions.

